Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-05-24 src/tf-cutcell-comparison/fig-meshes.tex
plot GW sampleLine and meshes

\setlength{\parindent}{0pt}
\begin{document}
\TPMargin{2pt}
\textblockcolour{white}
\begin{textblock}{0.5}(2.7,13.8)
\normalsize
(a)
\end{textblock}
\begin{textblock}{1}(8,13.8)
\normalsize
(b)
\end{textblock}
\begin{textblock}{1}(13.3,13.8)
\normalsize
(c)
\end{textblock}
\includegraphics{../mesh-btf-resting/constant/mesh.pdf}
\includegraphics{../mesh-sleve-resting/constant/mesh.pdf}
\includegraphics{../mesh-snapCol-resting/constant/mesh.pdf}
\end{document}

>>>>

\setlength{\parindent}{0pt}
\begin{document}
\TPMargin{2pt}
\textblockcolour{white}
\begin{textblock}{0.5}(2.7,13.8)
\normalsize
(a)
\end{textblock}
\begin{textblock}{1}(8,13.8)
\normalsize
(b)
\end{textblock}
\begin{textblock}{1}(13.3,13.8)
\normalsize
(c)
\end{textblock}
\includegraphics{../resting-mesh-btf/constant/mesh.pdf}
\includegraphics{../resting-mesh-sleve/constant/mesh.pdf}
\includegraphics{../resting-mesh-cutCell/constant/mesh.pdf}
\end{document}
